---
title: "ProcessVisCluster"
author: "Katie Rhodes"
date: "3/2/2021"
output: html_document
---

```{r}
library(Seurat)
```

load in filtered, normalized basal bone marrow count matrix
```{r}
dat<- read.table("/home/klrhodes/TusiTest/GSM2388072_basal_bone_marrow.filtered_normalized_counts.csv.gz", header=T, row.names=1, sep = ",")
```

check data structure
```{r}
dim(dat)
```

```{r}
head(dat)
```

```{r}
unique(dat$seq_run_id)
```
Two sequencing runs. In the paper methods they mention some batch effects likely due to sequencing depth. For now, I'm not going to deal with that-- will check whether it could be causing problems down the road

```{r}
unique(dat$library_id)
```

```{r}
unique(dat$pass_filter)
```
These are the already filtered set of cells, so they all pass the filter

I believe genes have already been filtered as well.  lets make it a Seurat object and look at some QC metrics:

```{r}
#transpose to rows are genes and cells are columns
dat<- t(dat)
meta<- dat[1:4,]
meta<- as.data.frame(t(meta))

obj<- CreateSeuratObject(dat[5:nrow(dat),], meta.data = meta)
```

```{r}
head(obj)
```

check some QC metrics
```{r}
obj[['percent.mt']]<- PercentageFeatureSet(obj, pattern = '^mt.')
VlnPlot(obj, features = c("nCount_RNA", "nFeature_RNA", "percent.mt"), pt.size = 0.2)
```

So, cells have clearly been filtered for mt percentage (less than 10%). I also don't see obvious signs of doublets in the numbers of counts or features, but I'll check again after clustering. 

I believe these counts are already normalized, so proceed to finding variable features
```{r}
obj<- FindVariableFeatures(obj, selection.method = "vst", nfeatures=2000)
```

```{r}
#scaling data
all.genes<- rownames(obj)
obj<- ScaleData(obj, features=all.genes)
```

```{r}
obj<- RunPCA(obj, features=VariableFeatures(obj))
```

```{r}
DimPlot(obj, reduction="pca")
```

```{r}
ElbowPlot(obj)
```

I'm gonna move forward with 15 PCs here

```{r}
obj<- FindNeighbors(obj, dims = 1:15)
obj<- FindClusters(obj, resolution = 0.5)
obj<- RunUMAP(obj, dims=1:15)
```
```{r}
DimPlot(obj, reduction="umap")
```

```{r}
DimPlot(obj, reduction="umap", group.by = "seq_run_id")
```

okay yeah so there's the batch effect. I checked and Tusi et al fix this by finding variable features in just the first seq run.  so I'll go back and change that.

