---
title: "DynamicVarianceTusi"
author: "Katie Rhodes"
date: "3/2/2021"
output: html_document
---
```{r}
library(Seurat)
library(dplyr)
library(stats)
```

```{r}
obj<- readRDS("/home/klrhodes/TusiTest/PostProcessObj.Rmd")
```

For this analysis, I'll really only be interested in Transcription Factors. Any gene COULD be involved with fate mechanism, but theres a lot we already know about the action of TFs, plus its (relatively) easy to guess what their downstream effects are. 

I grabbed the go_id information for all genes in this data set using biomaRt (check the biomart markdown)

load biomart info
```{r}
info<- read.csv("/home/klrhodes/TusiTest/Tusi_my_genes_infoFromBiomaRt_03022021.csv", header=T, row.names = 1)
```

```{r}
head(info)
```

```{r}
#keep only genes with go terms for  TFs--  GO:0003700

info_keep<- info[info$GO == "GO:0003700",]

feat_keep<- rownames(obj)[(rownames(obj) %in% info_keep$mgi)]

length(feat_keep)
```

```{r}
obj<- subset(obj, features = feat_keep)
```

```{r}
Idents(obj)<- 'RNA_snn_res.1.5'

#subset data from clusters of interest

#assumed megakaryocyte and erythroid progenitors
sub.clust8<- subset(obj, idents = '8')

#early erythroid
sub.clust10<- subset(obj, idents = '10')

#megakaryocyte
sub.clust9<- subset(obj, idents = '9')

#MPP
sub.clust6<- subset(obj, idents = '6')
```


Test to see if variance in each TF gene is different between clusters
```{r}
#isolate count matrix for each subset, make a df with a column for cluster id
clust10<- sub.clust10@assays$RNA@counts #179 cells
clust9<- sub.clust9@assays$RNA@counts #180 cells
clust8<- sub.clust8@assays$RNA@counts #225 cells
clust6<- sub.clust6@assays$RNA@counts #242 cells

cluster<- as.factor(c(rep("10", 179), rep("9", 180), rep("8", 225), rep("6", 242)))

count.df<- as.matrix(cbind(clust10,clust9, clust8, clust6))
count.df<- t(count.df)
count.df<- as.data.frame(cbind(cluster, count.df))

count.df$cluster<- as.factor(count.df$cluster)
```

now use fligner-killeen to test difference in variance in expression of each gene between clusters

```{r}
pvals<- NULL
for (i in 2:(ncol(count.df))){
  flig<- fligner.test(formula = colnames(count.df)[i]~cluster, count.df)
  pvals[i-1]<-flig$p.value
}

pvals
```

aand they are all so tiny that they round to zero. oop! 

I'm at time now, but here are the next things I would try:
- see if i can get R to stop rounding to 0 (not sure if this is a rounding issue when I extract the pvalue or an issue in the output of the fligner.test function)
-pairwise test instead of testing 4 groups at once to see if that reduces p values
-if still nothing, I might try something even more simplistic, calculating the variance for each gene in each cluster, calculating the pairwise difference between clusters, and then just ranking genes with the greatest increase in variance in the branch-point cluster. If TFs known to be important for fate decisions show up in that group, the others may have a mechanism of interest as well.

  


