---
title: "DynamicVarianceTusi"
author: "Katie Rhodes"
date: "3/2/2021"
output: html_document
---
```{r}
library(Seurat)
library(dplyr)
library(stats)
```

```{r}
obj<- readRDS("/home/klrhodes/TusiTest/PostProcessObj.Rmd")
```

For this analysis, I'll really only be interested in Transcription Factors. Any gene COULD be involved with fate mechanism, but theres a lot we already know about the action of TFs, plus its (relatively) easy to guess what their downstream effects are. 

I grabbed the go_id information for all genes in this data set using biomaRt (check the biomart markdown)

load biomart info
```{r}
info<- read.csv("/home/klrhodes/TusiTest/Tusi_my_genes_infoFromBiomaRt_03022021.csv", header=T, row.names = 1)
```

```{r}
head(info)
```

```{r}
#keep only genes with go terms for  TFs--  GO:0003700

info_keep<- info[info$GO == "GO:0003700",]

feat_keep<- rownames(obj)[(rownames(obj) %in% info_keep$mgi)]

length(feat_keep)
```

```{r}
obj<- subset(obj, features = feat_keep)
```

```{r}
Idents(obj)<- 'RNA_snn_res.1.5'

#subset data from clusters of interest

#assumed megakaryocyte and erythroid progenitors
sub.clust8<- subset(obj, idents = '8')

#early erythroid
sub.clust10<- subset(obj, idents = '10')

#megakaryocyte
sub.clust9<- subset(obj, idents = '9')

#MPP
sub.clust6<- subset(obj, idents = '6')
```


Test to see if variance in each TF gene is different between clusters
```{r}

```

